PWD.KAZ

### 2019-08-15 results/PWD.KAZ.BivData.Rmd
added and curated abunch of bivalent data. started some analysis

@@

#DONT LOAD MLH1 yet -- keep these seperate for now
#load(file="~./MLH1repo/data/MLH1/MLH1_data_setup_62419.RData")
#MLH1_data_setup_62419.RData
#KAZ_male_data = read.csv("~./data/KAZ_BivData.csv")
meta.data.file2 = read.csv("~./MLH1repo/data/Mouse_MetaData_6.12.19.csv", header = TRUE)

#1. Curated Data
#PWD set 4 mice, ~100 objs each)
PWD_curate_BivData.full =
  read.csv("~./MLH1repo/data/BivData/Merged_Curate_PWD_BivData.csv", header = TRUE)
#remove bad segmentation
PWD_curate_BivData <- PWD_curate_BivData.full[PWD_curate_BivData.full$SC.pass == 1,]

#KAZ 3 mice >200 objs each
KAZ_curate_BivData.full =
  read.csv("~./MLH1repo/data/BivData/curate_KAZ_BivData.csv", header = TRUE)
KAZ_curate_BivData <- KAZ_curate_BivData.full[KAZ_curate_BivData.full$SC.pass == 1,]

#merged KAZ and PWD
curate_BivData <- rbind(KAZ_curate_BivData, PWD_curate_BivData)

@@

#make indevidal DFs by strain just in case...
PWD.BivData.Hand_measures <- HandMeasures_BivData[HandMeasures_BivData$strain == "PWD",]
KAZ.BivData.Hand_measures <- HandMeasures_BivData[HandMeasures_BivData$strain == "KAZ",]
```

ToDo:
  -add in IFD calqs
  -add rbar calqs
  -make the basic plots ect

@@

#merg4.PWD_curate_BivData <-    #remove "avergeRED", numberCrossOvers
#merg4.PWD_hand_measure_BivData.full <- #manual.blobject.name

#auto.curate
auto.c_names <- c("fileName","centromere_ABS_Position","centromere_PER_Position",  "chromosomeLength","boxNumber","Obj.ID","SC.pass","foci.pass","curated.1pass.0fail.","curation.notes","hand.foci.count","Foci1","Foci2","Foci3" ,"mouse", "strain","sex","category")
new.DF <- curate_BivData[ , auto.c_names, drop = TRUE]

@@

#make WHOLE CELL DF

#some cleanup may be required for the manual data; remove all XY, mark chrm classes for all 
#make better variable name
Auto.Man_BivData_cells <- ddply(Auto.Man_BivData, c("fileName"), summarise,
                    number = length(Obj.ID),
                    #make the rank or
                     maxChrm_length = max(chromosomeLength),
                    maxChrm_boxNumber = boxNumber[which.max(chromosomeLength)]

@@

#make PWD and KAZ specific melt.DF ... if you want

#make whole cell melt
whole.cell_melt.DF <- Auto.Man_BivData.melt[Auto.Man_BivData.melt$fileName %in% whole.cell.list,]
#add rank to these measures
whole.cell_melt.DF <- ddply(whole.cell_melt.DF, .(fileName), transform, rank = rank(chromosomeLength,ties.method ="min")-1)
```

@@

save.image("~./MLH1repo/data/BivData/PWD.KAZ_BivData_data.RData")
```

@@

kk <- ggplot(data=bin.short.PWD, aes(x=mouse,y=chromosomeLength))+geom_jitter(width = 0.25)+ggtitle("short bins")

@@

@@

SC.PWD <- ggplot(data = PWD_curate_BivData, aes(color=fileName,x=mouse, y= chromosomeLength))+geom_jitter()+theme(legend.position="none")+ylim(c(35,150))+ggtitle("PWD SC lengths")
#the SC range is 45 - 150 (for PWD)

SC.KAZ <- ggplot(data = KAZ_curate_BivData, aes(color=fileName,x=mouse, y= chromosomeLength))+geom_jitter()+
  theme(legend.position="none")+ylim(c(35,150))+ggtitle("KAZ SC lengths")
#can I add the means?

@@

KAZ_mean_SC <- ddply(KAZ_curate_BivData, c("mouse"), summarise,

@@

PWD_mean_SC <- ddply(PWD_curate_BivData, c("mouse"), summarise,

@@

t.test(KAZ_curate_BivData$chromosomeLength,PWD_curate_BivData$chromosomeLength)

@@

the PWD has longer means

@@

KAZ.length.by.class <- ggplot(data=KAZ_whole.cell.BivData, aes(x=fileName,y=chromosomeLength))+geom_jitter(width = 0.25, aes(color=as.factor(hand.foci.count), shape=mouse))+ggtitle("PWD full cell SC lengths")

@@

#10mar15_PWD_m1: 13w
#10mar15_PWD_m2: 13w
#18may15_PWD_m1:  7w -- use this one
#18may15_PWD_m2: 7w  (seems like not all of the images were run through the algorithm)

@@

@@

#isolate the 2COs
#total Bivdata
KAZ.2COs <- KAZ.auto.man_BivData[KAZ.auto.man_BivData$hand.foci.count == 2,]
PWD.2COs <- PWD.auto.man_BivData[PWD.auto.man_BivData$hand.foci.count == 2,]

@@

@@

IFDs.ABS <- ggplot(data=all.2CO, aes(x=mouse,y=IFD1_ABS))+geom_jitter(width = 0.25, aes(color=as.factor(fileName) ))+ggtitle("raw IFD Distributions")+geom_boxplot(alpha = 0.6)+facet_wrap(~strain)+  theme(legend.position="none", axis.text.x = element_text(angle = 90, hjust = 1) )

IFDs.PER <- ggplot(data=all.2CO, aes(x=mouse,y=IFD1_PER))+geom_jitter(width = 0.25, aes(color=as.factor(fileName) ))+ggtitle("norm IFD Distributions")+geom_boxplot(alpha = 0.6)+facet_wrap(~strain)+theme(legend.position="none")

@@

```{r makeKAZ.curate.list, echo=FALSE}
#write out list for initial quality control and subsetting
#remove centromere_PER > .2
KAZ.Biv.curate.list <- KAZ_bivData[KAZ_bivData$centromere_PER_Position < 0.2,]#3123

#remove chrmLength > 150? 200
KAZ.Biv.curate.list <- KAZ.Biv.curate.list[KAZ.Biv.curate.list$chromosomeLength < 300, ]#not completely sure 300 is probably the max length is the best length
#3117

table(KAZ.Biv.curate.list$mouse)
#7 mice: 11jan18_KAZ_m4(9w), 1feb18_KAZ_m1(11w), 11jan18_KAZ_m3(9w), and 11jan18_KAZ_m1(43w) have good MLH1

cur11jan18_KAZ_m4 <- KAZ.Biv.curate.list[KAZ.Biv.curate.list$mouse == "11jan18_KAZ_m4",]

cur11jan18_KAZ_m4$Obj.ID <- paste(cur11jan18_KAZ_m4$fileName, cur11jan18_KAZ_m4$boxNumber, sep = "_")

write.table(cur11jan18_KAZ_m4, "~./MLH1repo/results/curate_cur11jan18_KAZ_m4_BivData.txt", sep="\t", row.names = FALSE)

>>>>

#todo -- load in female data

@@

#DONT LOAD MLH1 yet -- keep these seperate for now
load(file="~./MLH1repo/data/MLH1/MLH1_data_setup_62419.RData")
#MLH1_data_setup_62419.RData
#KAZ_male_data = read.csv("~./data/KAZ_BivData.csv")
meta.data.file2 = read.csv("~./MLH1repo/data/Mouse_MetaData_6.12.19.csv", header = TRUE)

#1. Curated Data
PWD.KAZ_curate_BivData.full =
  read.csv("~./MLH1repo/data/BivData/Merged_Curate_PWD.KAZ_BivData.csv", header = TRUE)

PWD.KAZ_curate_BivData.full <- PWD.KAZ_curate_BivData.full[!(is.na(PWD.KAZ_curate_BivData.full$SC.pass) ),]

PWD.KAZ_curate_BivData <- PWD.KAZ_curate_BivData.full[PWD.KAZ_curate_BivData.full$SC.pass == 1,]

#PWD set 4 mice, ~100 objs each)
#PWD_curate_BivData.full =
#  read.csv("~./MLH1repo/data/BivData/Merged_Curate_PWD_BivData.csv", header = TRUE)
#remove bad segmentation
#PWD_curate_BivData <- PWD_curate_BivData.full[PWD_curate_BivData.full$SC.pass == 1,]

#KAZ 3 mice >200 objs each
#KAZ_curate_BivData.full =
#  read.csv("~./MLH1repo/data/BivData/curate_KAZ_BivData.csv", header = TRUE)#not sure where to find this file
#KAZ_curate_BivData <- KAZ_curate_BivData.full[KAZ_curate_BivData.full$SC.pass == 1,]

#merged KAZ and PWD
#curate_BivData <- rbind(KAZ_curate_BivData, PWD_curate_BivData)

#incorporate female data
PWD.KAZ_BivData_8.14.19_curated.full = 
  read.csv("~./MLH1repo/data/BivData/PWD.KAZfemale_curated_8.15.19.csv", header = TRUE)#740
#merge and check that they have the same columns
str(PWD.KAZ_BivData_8.14.19_curated.full)

PWD.KAZ_BivData <- PWD.KAZ_BivData_8.14.19_curated.full[!(is.na(PWD.KAZ_BivData_8.14.19_curated.full$SC.pass) ),]

PWD.KAZ_BivData <- PWD.KAZ_BivData[PWD.KAZ_BivData$SC.pass == 1,]

str(PWD.KAZ_BivData)

curate_PWD.KAZ_BivData_M.F <- rbind(PWD.KAZ_curate_BivData, PWD.KAZ_BivData)
str(curate_PWD.KAZ_BivData_M.F)

#forgot why I'm removing these
#curate_PWD.KAZ_BivData_M.F <- curate_PWD.KAZ_BivData_M.F[curate_PWD.KAZ_BivData_M.F$Obj.ID != "25feb15_8oct14_PWD_f8_sp1_1_rev_19",]
#curate_PWD.KAZ_BivData_M.F <- curate_PWD.KAZ_BivData_M.F[curate_PWD.KAZ_BivData_M.F$Obj.ID != "9aug15_23apr15_PWD_f2_sp1_9.1_rev_15",]
#curate_PWD.KAZ_BivData_M.F <- curate_PWD.KAZ_BivData_M.F[curate_PWD.KAZ_BivData_M.F$Obj.ID != "9aug15_23apr15_PWD_f2_sp1_9.1_rev_18",]

#male+female KAZ and PWD bivData
source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
curate_PWD.KAZ_BivData_M.F <- add_mouse(curate_PWD.KAZ_BivData_M.F)
curate_PWD.KAZ_BivData_M.F <- add_category(curate_PWD.KAZ_BivData_M.F)
curate_PWD.KAZ_BivData_M.F <- add_strain(curate_PWD.KAZ_BivData_M.F)
curate_PWD.KAZ_BivData_M.F <- add_sex(curate_PWD.KAZ_BivData_M.F)

@@

#make indevidal DFs by strain just in case...
#PWD.BivData.Hand_measures <- HandMeasures_BivData[HandMeasures_BivData$strain == "PWD",]
#KAZ.BivData.Hand_measures <- HandMeasures_BivData[HandMeasures_BivData$strain == "KAZ",]
```

ToDo:
  -add in IFD calqs
  -add rbar calqs
  -make the basic plots ect
  -analyze female patterns

  -what are the distributions of female IFDs and nrm IFDs
  -what are the proportions of chrm classes?

@@

#merg4.PWD_curate_BivData <-    #remove "avergeRED", numberCrossOvers
#merg4.PWD_hand_measure_BivData.full <- #manual.blobject.name
#curate_PWD.KAZ_BivData_M.F

#auto.curate
auto.c_names <- c("fileName","centromere_ABS_Position","centromere_PER_Position",  "chromosomeLength","boxNumber","Obj.ID","SC.pass","foci.pass","curated.1pass.0fail.","curation.notes","hand.foci.count","Foci1","Foci2","Foci3" ,"mouse", "strain","sex","category")
new.DF <- curate_PWD.KAZ_BivData_M.F[ , auto.c_names, drop = TRUE]

@@

table(Auto.Man_BivData$hand.foci.count[Auto.Man_BivData$sex == "female"], Auto.Man_BivData$strain[Auto.Man_BivData$sex == "female"])

#remove empty cells
#remove extra empty rows
Auto.Man_BivData <- Auto.Man_BivData[!(is.na(Auto.Man_BivData$SC.pass) | Auto.Man_BivData$SC.pass == ""), ]
Auto.Man_BivData <- Auto.Man_BivData[(Auto.Man_BivData$SC.pass == "1"), ]

#make WHOLE CELL DF
#some cleanup may be required for the manual data; remove all XY, mark chrm classes for all 
#make better variable name
Auto.Man_BivData_cells <- ddply(Auto.Man_BivData, c("fileName"), summarise,
                    number = length(Obj.ID),
                    #make the rank or
                     maxChrm_length = max(chromosomeLength),
                    maxChrm_boxNumber = boxNumber[which.max(chromosomeLength)]

@@

#make PWD and KAZ specific melt.DF ... if you want
#make whole cell melt
whole.cell_melt.DF <- Auto.Man_BivData.melt[Auto.Man_BivData.melt$fileName %in% whole.cell.list,]
#add rank to these measures
whole.cell_melt.DF <- ddply(whole.cell_melt.DF, .(fileName), transform, rank = rank(chromosomeLength,ties.method ="min")-1)
```

```{r Female.Nrm.Pos}
melt.PWD.female  <- Auto.Man_BivData.melt[(Auto.Man_BivData.melt$sex == "female") & (Auto.Man_BivData.melt$strain == "PWD"),]
melt.KAZ.female <- Auto.Man_BivData.melt[(Auto.Man_BivData.melt$sex == "female") & (Auto.Man_BivData.melt$strain == "KAZ"),]

nPWD.F.obs <- ddply(.data=melt.PWD.female, 
                 .(hand.foci.count),
                 summarize, 
                 n=paste("n =", length(unique(Obj.ID))))

nKAZ.F.obs <- ddply(.data=melt.KAZ.female, 
                 .(hand.foci.count),
                 summarize, 
                 n=paste("n =", length(unique(Obj.ID))))

#figures for foci positions
melt.plot.PWD.female    <- ggplot(melt.PWD.female,
              aes(x=nrmFoci.pos, fill=nrmFoci.Type) ) +

  geom_histogram(alpha= 0.5,stat = "bin", position= "identity")+
 facet_wrap(~ hand.foci.count, scales="free", ncol=1)+ggtitle("PWD female norm foci positions")+
 geom_text(data=nPWD.F.obs, aes(x=.25, y=7, label=n), 
         colour="black", inherit.aes=FALSE, parse=FALSE)+xlim(c(0,1)) + ylim(c(0,13))

melt.plot.KAZ.female    <- ggplot(melt.KAZ.female,
              aes(x=nrmFoci.pos, fill=nrmFoci.Type) ) + 
  geom_histogram(alpha= 0.5,stat = "bin", position= "identity")+
 facet_wrap(~ hand.foci.count, scales="free", ncol=1)+ggtitle("KAZ female norm foci positions")+
 geom_text(data=nKAZ.F.obs, aes(x=.25, y=7, label=n), 
         colour="black", inherit.aes=FALSE, parse=FALSE)+xlim(c(0,1)) + ylim(c(0,13))

#t.tests for mean F positions
CO1.F1.t.test <- t.test(melt.KAZ.female$nrmFoci.pos[(melt.KAZ.female$nrmFoci.Type == "nrm.F1.pos") &(melt.KAZ.female$hand.foci.count == 1)],
                        melt.PWD.female$nrmFoci.pos[(melt.PWD.female$nrmFoci.Type == "nrm.F1.pos") &(melt.PWD.female$hand.foci.count == 1)]  )

CO2.F1.t.test <- t.test(melt.KAZ.female$nrmFoci.pos[(melt.KAZ.female$nrmFoci.Type == "nrm.F1.pos") &(melt.KAZ.female$hand.foci.count == 2)],
                        melt.PWD.female$nrmFoci.pos[(melt.PWD.female$nrmFoci.Type == "nrm.F1.pos") &(melt.PWD.female$hand.foci.count == 2)] )

CO2.F2.t.test <- t.test(melt.KAZ.female$nrmFoci.pos[(melt.KAZ.female$nrmFoci.Type == "nrm.F2.pos") &(melt.KAZ.female$hand.foci.count == 2)],
                        melt.PWD.female$nrmFoci.pos[(melt.PWD.female$nrmFoci.Type == "nrm.F2.pos") &(melt.PWD.female$hand.foci.count == 2)] )
#none of the positions are significantly different

```{r}
#another set of plots

PWD.female <- Auto.Man_BivData[(Auto.Man_BivData$strain == "PWD") & (Auto.Man_BivData$sex == "female"), ]
KAZ.female <- Auto.Man_BivData[(Auto.Man_BivData$strain == "KAZ") & (Auto.Man_BivData$sex == "female"), ]

#figures for foci positions
PWD.female_foci1_foci2_plot    <- ggplot(PWD.female[PWD.female$hand.foci.count == 2,],  aes(x=Foci1, y=Foci2, color = chromosomeLength) ) + geom_point()+
  geom_abline(intercept = .5, slope = 1, color="red")+xlim(c(0,100)) + ylim(c(0,200))+ggtitle("PWD female")+scale_colour_gradientn(colours=rainbow(5))
#the 5 in rainbow increases the difference between colors

KAZ.female_foci1_foci2_plot    <- ggplot(KAZ.female[KAZ.female$hand.foci.count == 2,],  aes(x=Foci1, y=Foci2, color = chromosomeLength) ) + geom_point()+geom_abline(intercept = .5, slope = 1, color="red")+xlim(c(0,100)) + ylim(c(0,200))+ggtitle("KAZ female")+scale_colour_gradientn(colours=rainbow(5))

#make points slightly bigger

@@

save.image("~./MLH1repo/data/BivData/PWD.KAZ_BivData_data_8.14.19.RData")
```

@@

@@

##kk <- ggplot(data=bin.short.PWD, aes(x=mouse,y=chromosomeLength))+geom_jitter(width = 0.25)+ggtitle("short bins")

@@

table(Auto.Man_BivData$sex)

PWD.Auto.Man_BivData <- Auto.Man_BivData[Auto.Man_BivData$strain == "PWD",]

SC.PWD <- ggplot(data = PWD.Auto.Man_BivData, aes(color=fileName,x=mouse, y= chromosomeLength))+geom_jitter()+theme(legend.position="none")+ylim(c(35,250))+ggtitle("PWD SC lengths") +facet_wrap(~sex)
#the SC range is 45 - 150 (for PWD)

KAZ.Auto.Man_BivData <- Auto.Man_BivData[Auto.Man_BivData$strain == "KAZ",]

SC.KAZ <- ggplot(data = KAZ.Auto.Man_BivData, aes(color=fileName,x=mouse, y= chromosomeLength))+geom_jitter()+
  theme(legend.position="none")+ylim(c(35,250))+ggtitle("KAZ SC lengths")+facet_wrap(~sex)
#can I add the means?

@@

str(PWD.Auto.Man_BivData)

KAZ_mean_SC <- ddply(KAZ.Auto.Man_BivData, c("mouse","sex"), summarise,

                    boxs.IDd = max(as.numeric(boxNumber)),
                    nboxes_passed = length(as.numeric(boxNumber)),
                    pass_rate = nboxes_passed/boxs.IDd,#I don't know if pass rate is working

@@

PWD_mean_SC <- ddply(PWD.Auto.Man_BivData, c("mouse","sex"), summarise,

                    boxs.IDd = max(as.numeric(boxNumber)),
                    nboxes_passed = length(as.numeric(boxNumber)),
                    pass_rate = nboxes_passed/boxs.IDd,

@@

t.test(KAZ.Auto.Man_BivData$chromosomeLength[KAZ.Auto.Man_BivData$sex == "male"],PWD.Auto.Man_BivData$chromosomeLength[PWD.Auto.Man_BivData$sex == "male"]   )#p is small

t.test(KAZ.Auto.Man_BivData$chromosomeLength[KAZ.Auto.Man_BivData$sex == "female"],PWD.Auto.Man_BivData$chromosomeLength[PWD.Auto.Man_BivData$sex == "female"]   )#p not as small

@@

The PWD has longer mean SC. Female KAZ are a bit larger. PWD female aren't as small.

@@

KAZ.length.by.class <- ggplot(data=KAZ_whole.cell.BivData, aes(x=fileName,y=chromosomeLength)) + geom_jitter(width = 0.25, aes(color=as.factor(hand.foci.count), shape=mouse))+ggtitle("PWD full cell SC lengths")

@@

#10mar15_PWD_m1: 13w
#10mar15_PWD_m2: 13w

#18may15_PWD_m1:  7w -- use this one... these are good cells
#18may15_PWD_m2: 7w  (seems like not all of the images were run through the algorithm)

#test the correlation of F points between cells
#but make sure

#all.2CO
#all.2CO_PWD

Foci_Corr.PWD <- ggplot(data=whole.cell.2CO.PWD, aes(x=Foci1.PER, y=Foci2.PER))+geom_point( aes(color=as.factor(rank) ) )+ggtitle("correletaion of Nrm Foci Posisitons")+facet_wrap(~mouse) +ylim(c(0,1))+xlim(c(0,1))

#theme(legend.position="none")

whole.cell.KAZ$Foci1.PER <- whole.cell.KAZ$Foci1 / whole.cell.KAZ$chromosomeLength
whole.cell.KAZ$Foci2.PER <- whole.cell.KAZ$Foci2 / whole.cell.KAZ$chromosomeLength
whole.cell.KAZ$Foci3.PER <- whole.cell.KAZ$Foci3 / whole.cell.KAZ$chromosomeLength

whole.cell.KAZ.2CO <- whole.cell.KAZ[whole.cell.KAZ$hand.foci.count == 2,]
whole.cell.KAZ.2CO <- droplevels(whole.cell.KAZ.2CO)

whole.cell.KAZ.2CO <- whole.cell.KAZ.2CO[!(is.na(whole.cell.KAZ.2CO$Foci1.PER) | whole.cell.KAZ.2CO$Foci1.PER == ""), ]

Foci_Corr.KAZ <- ggplot(data=whole.cell.KAZ.2CO, aes(x=Foci1.PER, y=Foci2.PER))+geom_point(aes(color=interaction(fileName,mouse) ) )+ggtitle("correletaion of Nrm Foci Posisitons")+facet_wrap(~mouse) +ylim(c(0,1))+xlim(c(0,1))

whole.cell.2CO.PWD <- whole.cell.2CO.PWD[whole.cell.2CO.PWD$hand.foci.count == 2,]
whole.cell.2CO.PWD <- droplevels(whole.cell.2CO.PWD)

table(whole.cell.2CO.PWD$hand.foci.count)

Foci_Corr.PWD2 <- ggplot(data=whole.cell.2CO.PWD, aes(x=Foci1.PER, y=Foci2.PER))+geom_point(aes(color=interaction(fileName,mouse) ) )+ggtitle("correletaion of Nrm Foci Posisitons")+facet_wrap(~mouse) +ylim(c(0,1))+xlim(c(0,1))

Foci_Corr.PWD2 <- ggplot(data=whole.cell.2CO.PWD, aes(x=Foci1.PER, y=Foci2.PER))+geom_point(aes(color=interaction(fileName,mouse) ) )+ggtitle("correletaion of Nrm Foci Posisitons")+facet_wrap(~mouse) +ylim(c(0,1))+xlim(c(0,1))

PWD.1 <- whole.cell.2CO.PWD[whole.cell.2CO.PWD$mouse == "1mar15_PWD_m1",]

PWD.1$Per2_Per1 <- PWD.1$Foci2.PER - PWD.1$Foci1.PER

Foci_Corr.PWD99 <- ggplot(data=PWD.1, aes(x=Foci1.PER, y=Foci2.PER))+geom_point(aes(color=interaction(fileName) ) )+ggtitle("correletaion of Nrm Foci Posisitons")+facet_wrap(~fileName) +ylim(c(0,1))+xlim(c(0,1))+
  geom_abline(intercept = .5, slope = 1, color="red")+
  geom_abline(intercept = 0, slope = 1)

#making slopes of 1 (then they are horizontal)
#the slope of blue lines doesn't fit that slope

#1:1 slope should be interperted as consistant process / rule within cell

#strong pos correlation of Foci positions

Foci_Corr.PWD88 <- ggplot(data=PWD.1, aes(x=Foci1, y=Foci2))+geom_point(aes(color=interaction(rank) ) )+ggtitle("correletaion of Nrm Foci Posisitons")+facet_wrap(~fileName) 
#not sure what the raw IFD pattern shows
#I should learn to add daigonal lines as bench marks

+ylim(c(0.6,1))+xlim(c(0,1))

#comparing KAZ, it looks like Foci 1 is further from the centromere (towards the middle)
#

#whole.cell.2CO.PWD -- I can fill color by rank, .. (2COs are biased to longer chrms, but there are some shorter ones

blah2 <- ggplot(data=all.2CO, aes(x=Foci1,y=Foci2))+geom_jitter(width = 0.25, aes(color=mouse))+ggtitle("correletaion of Foci Posisitons")+facet_wrap(~strain)+ theme(legend.position="none")+ylim(c(0,150))+xlim(c(0,90))

#plot stacked IFD lines -- linking the foci

#Can I calculate esitmated rank?

@@

find a way to analyze the 2CO / IFD for the female data

@@

#Auto.Man_BivData
#PWD.Auto.Man_BivData
#KAZ.Auto.Man_BivData

ookk <- ggplot(data = Auto.Man_BivData[Auto.Man_BivData$sex == "female",], aes(x=chromosomeLength))+geom_density(aes(fill=hand.foci.count), alpha = .3)+facet_wrap(strain~sex)
#there are too many bad levels for hand.foci.count

ookk2 <- ggplot(data = Auto.Man_BivData[Auto.Man_BivData$sex == "female",], aes(x=chromosomeLength))+geom_histogram(aes(fill=hand.foci.count), alpha = .3)+facet_wrap(strain~sex)

#isolate the 2COs
#total Bivdata
KAZ.2COs <- KAZ.Auto.Man_BivData[KAZ.Auto.Man_BivData$hand.foci.count == 2,]
PWD.2COs <- PWD.Auto.Man_BivData[PWD.Auto.Man_BivData$hand.foci.count == 2,]

@@

table(Auto.Man_BivData$mouse[Auto.Man_BivData$sex == "female"])

table(all.2CO$mouse[all.2CO$sex=="female"])

#main female mice for comparison
#23apr15_PWD_f2, 23apr15_PWD_f2

@@

IFDs.ABS <- ggplot(data=all.2CO, aes(x=mouse,y=IFD1_ABS))+geom_jitter(width = 0.25, aes(color=as.factor(fileName) ))+ggtitle("raw IFD Distributions")+geom_boxplot(alpha = 0.6)+facet_wrap(sex~strain)+  theme(legend.position="none", axis.text.x = element_text(angle = 90, hjust = 1) )

IFDs.ABS.22 <- ggplot(data=all.2CO, aes(x=mouse,y=IFD1_ABS, fill=interaction(strain,sex)))+geom_jitter(width = 0.25)+ggtitle("raw IFD Distributions")+geom_boxplot(alpha = 0.6)+  theme(legend.position="none", axis.text.x = element_text(angle = 90, hjust = 1) )

IFDs.PER <- ggplot(data=all.2CO, aes(x=mouse,y=IFD1_PER))+geom_jitter(width = 0.25, aes(color=as.factor(fileName) ))+ggtitle("norm IFD Distributions")+geom_boxplot(alpha = 0.3)+facet_wrap(sex~strain)+theme(legend.position="none")+theme(legend.position="none", axis.text.x = element_text(angle = 90, hjust = 1) )

#remove mice with very few observations?

@@

```{r makeKAZ.curate.list, echo=FALSE}
#write out list for initial quality control and subsetting
#remove centromere_PER > .2
#KAZ.Biv.curate.list <- KAZ_bivData[KAZ_bivData$centromere_PER_Position < 0.2,]#3123
#remove chrmLength > 150? 200
#KAZ.Biv.curate.list <- KAZ.Biv.curate.list[KAZ.Biv.curate.list$chromosomeLength < 300, ]#not completely sure 300 is probably the max length is the best length
#3117
#table(KAZ.Biv.curate.list$mouse)
#7 mice: 11jan18_KAZ_m4(9w), 1feb18_KAZ_m1(11w), 11jan18_KAZ_m3(9w), and 11jan18_KAZ_m1(43w) have good MLH1
#cur11jan18_KAZ_m4 <- KAZ.Biv.curate.list[KAZ.Biv.curate.list$mouse == "11jan18_KAZ_m4",]
#cur11jan18_KAZ_m4$Obj.ID <- paste(cur11jan18_KAZ_m4$fileName, cur11jan18_KAZ_m4$boxNumber, sep = "_")
#write.table(cur11jan18_KAZ_m4, "~./MLH1repo/results/curate_cur11jan18_KAZ_m4_BivData.txt", sep="\t", row.names = FALSE)
```
